---
title: "R Notebook"
output: html_notebook
---
#Question 1
```{r}
library(tidyverse)
library(CodeClanData)
```
```{r}
drinks_content
view(drinks_content)
nrow(drinks_content)
ncol(drinks_content)
dim(drinks_content)
```
#Question 2
```{r}
drinks_content %>% 
select(Beverage_category, Beverage, Beverage_prep, Calories) %>% 
  filter(is.na(Calories)) %>% 
  summarise(count_of_missing_calories = n())
```
#Question 3
```{r}
drinks_calories <- drinks_content %>% 
mutate(calorie_diff = Calories - 135) 
```
#Question 4 
```{r}
most_calories <- drinks_calories %>% 
group_by(Beverage_category) %>% 
  summarise(mean_calories = mean(Calories)) %>% 
  arrange(desc(mean_calories)) %>% 
  head(3)
```
```{r}
most_calories
```
#Question 5
```{r}
average_bev_prep <- drinks_calories %>% 
  group_by(Beverage_prep) %>% 
  summarise(mean_cals = mean(Calories)) %>% 
  arrange(desc(mean_cals))
```
```{r}
average_bev_prep
```

#Question 6
```{r}
avg_calories <- drink_calories %>%
                  summarise(mean_calories = mean(Calories)) %>%
                  pull()

avg_calories 
```
```{r}
above_avg_calories <- average_bev_prep %>%
  filter(mean_cals >= avg_calories)

above_avg_calories
```
```{r}
average_bev_prep %>%
  mutate(is_greater_than_avg = mean_cals >= avg_calories) %>%
  filter(is_greater_than_avg == TRUE)
```

#Question 7

# can start by finding the drink with the lowest number of calories 
drink_calories %>%
  group_by(Beverage_category, Beverage, Beverage_prep) %>%
  summarise(min_calories = min(Calories)) %>%
  arrange(min_calories) %>%
  head(1)

# But this is a Tea and the answer specifically asked for coffee drink! So we will filter out this tea drink to get the lowest calorie coffee drink.


drink_calories %>%
  filter(Beverage_category != "Tazo® Tea Drinks") %>%
  group_by(Beverage_category, Beverage, Beverage_prep) %>%
  summarise(min_calories = min(Calories)) %>%
  arrange(min_calories) %>%
  head(1)