---
title: "R Notebook"
output: html_notebook
---
```{r}
library(tidyverse)
library(janitor)
library(GGally)
library(fastDummies)
library(ggfortify)
```
###1
```{r}
housing_prices <- read_csv("data/housing_prices.csv") 
```
```{r}
head(housing_prices)
```
###2
```{r}
ggpairs(housing_prices, columns = 4:5)
```
correlation of 0.934 i.e very strong positive

###3
```{r}
housing_prices <- housing_prices %>% 
  select(-total_bedrooms)

#what about populations and households??
```
###4
```{r}
housing_prices %>% 
  ggpairs()

housing_prices %>% 
  ggplot(aes(x = median_income,
             y = median_house_value))+
  geom_point()

housing_prices %>% 
  ggplot(aes(x = ocean_proximity,
             y = median_house_value))+
  geom_boxplot()
```
###5
```{r}
housing_prices <- housing_prices %>% 
  dummy_cols(select_columns = "ocean_proximity", remove_first_dummy = TRUE, remove_selected_columns = TRUE) #1H ocean is dummy variable
```

###6
```{r}
model_value_income <- lm(median_house_value ~ median_income, housing_prices)

summary(model_value_income)

autoplot(model_value_income)
```
median house value = 39987*median_income + 45457
effect of income on house value is statistically significant
my model with median income explains 41.29% of the changes in house value
for each 1 unit increase in income, house price increases by 39987

###7
```{r}
model_value_income_bay <- lm(median_house_value ~ median_income + `ocean_proximity_NEAR BAY`, housing_prices)

summary(model_value_income_bay)

autoplot(model_value_income_bay)
```
the median house value with an owner of income 8 by the bay will be worth: 399064

median_house_value = (39611.7*median_income) + (39611.7*ocean_proximity_NEAR BAY) + 42558.7

```{r}
39611.7*8 + 39611.7 + 42558.7
```

###8
```{r}
housing_prices <- housing_prices %>% 
  mutate(across(ocean_proximity_INLAND:`ocean_proximity_NEAR OCEAN`, as.logical))

model_inter <- lm(median_house_value ~ median_income + `ocean_proximity_NEAR BAY` + median_income:`ocean_proximity_NEAR BAY`, housing_prices)

summary(model_inter)

autoplot(model_inter)
```
interaction is not statistically justifed based on high p value
###9
```{r}
housing_prices %>%   
ggplot(aes(x = log(median_income),
             y = median_house_value, colour = `ocean_proximity_NEAR BAY`))+
  geom_point()+
  geom_smooth(method = "lm", se = FALSE)

```

